% !TEX root = ../main.tex
\documentclass[../main.tex]{subfiles}

\begin{document}
\title{
  For some small values of $a,b \in \Z$ the Galois group over $\Q$ of any factor of $x^n + ax + b$ is the full symmetric group for all $n$.
}
\maketitle
% \begin{abstract}
%   We show that the Galois group over $\Q$ of any factor of $x^n + ax + b$ is the full symmetric group for all $n \in \N$ and for all pairs $\left( a, b \right)$ in the list \InlineProvenCases
  
% \end{abstract}
\section{Introduction}
Let $f\left( x \right) = x^n + ax + b$ for some $a,b \in \Z$ and $n \in \N$.
If $ab = 0$ we can calculate the Galois group over $\Q$ of each factor of $f$ using Kummer's theory.
When $ab \neq 0$, most existing literature handles the case of an irreducible $f$, and focuses on finding sufficient conditions for its Galois group to be $S_n$.
For example, for all $n \in \N$, Selmer \cite{SelmerIrreducibility1956} showed that $x^n - x - 1$ is irreducible, and Nart and Vila \cite{NartVila1979} showed that its Galois group is $S_n$.
Uchida \cite{Uchida} and Yamamoto \cite{Yamamoto} showed already beforehand that if $f$ is irreducible, $n$ is prime then the Galois group of $f$ is $S_n$.
Nart and Vila \cite{NartVila1979} and Osada \cite{Osada1987TheGG} found some more general criteria.
%  and Cohen Movahhedi and Salinier (\cite{Cohen1997} and \cite{COHEN1999}) found even more general criteria that ensure primitivity of the Galois group.
However, fixing $a$ and $b$, except in the mentioned example of $x^n - x - 1$, each of these criteria includes somce congruence condition on $n$, leaving out a positive density of the natural numbers.

One reducable case that has been studied is the case $f\left( x \right) = x^n - 2x + 1$.
In this case, $f$ is a product of $x-1$ and the polynomial 
\[
  g\left( x \right) = x^{n-1} + x^{n-2} + \cdots + x - 1
\]
The roots of $g$ are the reciprocals of the generalized Fibonacci recurrence equation
\[
  h\left( x \right) = x^{n-1} - x^{n-2} - \cdots - x - 1
\]
which was shown by Miles \cite{Miles1960} and wolfram \cite{Wolfram1998} to be irreducible.
Therefore, $g$ is also irreducible and has the same Galois group as $h$.
For any odd value of $n$, the Galois group of $h$ was shown to be $S_{n-1}$ by Martin \cite{MARTIN2004213}.
Soroker and Shusterman and Zannier \cite[Appendix A]{Soroker_appendix_2017} proved that for any $n$, the field defined over $\Q$ by $h$ has no totally real subextension.
In fact, to prove that the Galois group of $g$ is $S_{n-1}$, we extended their result and showed that the field defined by $h$ has no nontrivial subextensions at all.

In this paper we proved the following results: 
\begin{thm}
  For any pair $\left( a, b \right)$ in the list 
  \begin{equation}
    \label{eq:the_list}
    \ProvenCases
  \end{equation}
  and for any $n \in \N$, the Galois group over $\Q$ of any factor of $x^n + ax + b$ is the full symmetric group.
  \begin{enumerate}
    \item If $\left( a, b \right) = \left( \pm 1, \pm 1 \right)$, then by substituting $x$ with $-x$ if necessary we can always reduce to one of the cases $\left( 1, 1 \right)$ or $\left( -1, -1 \right)$.
    In the first case $f$ factors as $x^2 + x + 1$ times an irreducible polynomial.
    \item If $\left( a, b \right) = \left( \pm 2, \pm 1 \right)$, then by substituting $x$ with $-x$ if necessary we can always reduce to one of the cases $\left( -2, 1 \right)$ or $\left( 2, -1 \right)$.
    In the first case $f$ factors as $x - 1$ times an irreducible polynomial.
    \item If $\left( a, b \right) = \left( \pm 1, \pm 2 \right)$, then by substituting $x$ with $-x$ if necessary we can always reduce to one of the cases $\left( 1, -2 \right)$ or $\left( -1, 2 \right)$.
    In the first case $f$ factors as $x - 1$ times an irreducible polynomial.
  \end{enumerate}
  Except of these three cases, for any pair $\left( a, b \right)$ in the list \eqref{eq:the_list} and for any $n \in \N$, $f$ is irreducible.
\end{thm} 
\editorial{Of course the factorization of $f$ in the cases $\left( 1, 1 \right)$ and $\left( -2, 1 \right)$ is not new, the only new thing is that the other cases are irreducible, I hope the statement does not give the wrong impression.
I think even the irreducibility in all of the other cases can be deduced from standard criteria, so maybe we should not state it as a theorem and find some other way to present it.}

We will present the startegy of the proof that the Galois group is $S_n$ in the cases where $f$ is irreducible.
The startegy for the reducible cases is similar.
We will first show the key fact, for any prime number $p$ that does not divide $ab$, and an embedding of $\overline{\Q}$ into $\overline{\Q_p}$ the image of the absolute inertia group of $\Q_p$ in the Galois group of $f$ is either trivial or generated by a transposition.
Assume towards contradiction that the Galois group of $f$ is not $S_n$.
It is well known that any primitive permutation group that contains a transposition is symmetric.
Therefore, either the Galois group of $f$ contains no transposition, in which case it follows from the key fact above that $f$ ramifies only above primes that divide $ab$, or the Galois group of $f$ is imprimitive.
In the latter case, we will show that it follows that $\Q\left[ x \right] / \left( f \right)$ has a nontrivial subextension that is ramified only above primes that divide $ab$.
Thus, in either case we will deduce that there is some subextension $\Q \subsetneq K \subseteq \Q\left[ x \right] / \left( f \right)$ that is ramified only above primes that divide $ab$.
Finally, in each of the cases we will find a constant bound for the $p$-adic valuation of the root discriminant of $K$.
In cases where the bound is good enough, the Odlyzko bound tells us that there are only finitely many number fields with root discriminant below the bound.
In cases where the bound is even better, that list is enumerated in the LMFDB \cite{lmfdb}.
If we are even luckier, there are very few number fields in this list that are ramified only above the primes that divide $ab$, and we can rule out by hand the possibility that each of these fields is contained in $\Q\left[ x \right] / \left( f \right)$.

% We showed that 
% \begin{enumerate}
%   \item the galois group of $\Q\left[ x \right] / \left( f \right)$ is primitive in and only if the latter has no nontrivial subextensions.
%   \item for any $p \not \mid ab$, any inertia group of a prime ideal above $p$ is either trivial or generated by a transposition.
% \end{enumerate}
% We used $(2)$ to show that any nontrivial subextension of $\Q\left[ x \right] / \left( f \right)$ is ramified only above primes that divide $ab$.
% Therefore, if we show that $\Q\left[ x \right] / \left( f \right)$ has no 
\end{document}